---
title: "Additional Analyses"
output: 
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
---

```{r setup, include=F}
knitr::opts_chunk$set(
  cache=T, comment=NA, warning=F, echo=T, error=F, 
  message=F, prompt=F, tidy=T, fig.height=4
  )
options(digits = 3, width = 120)
```

In what follows, please find the results of additional analyses. These include models, results without covariates, results with all participants (hence, including those removed due to speeding).

# Set-up

Load packages.

```{r r-setup, results='hide'}
# define packages
packages <- c("cowplot", "devtools", "faoutlier", "GGally", "kableExtra",
              "knitr", "lavaan", "magrittr", "MVN", "psych", "pwr", "quanteda",
              "semTools", "tidyverse")

# load packages
lapply(packages, library, character.only = TRUE, quietly = TRUE)
```

Load data.

```{r Data-Wrangling, cache=F}
# load workspace
load("data/workspace.rdata")
```

# VIF

In what follows, you can find estimations of variance inflation factors, which help gauge multicollinearity. Generally, values above 5 or even 10 are considered problematic. However, these are only rules of thumb, and multcollinearity can occour with lower values. Indeed, although the values reported below are not above 5, they are increased, suggesting that multicollinearity might be at play here, which the regular analyses also confirm.

```{r vif}
# Self-Efficacy
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
SE01_01 ~~ a*SE01_02
SE01_03 ~~ a*SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

self_eff ~ pri_con + grats_gen + pri_delib + trust_spec

# Covariates
GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
r_self_eff <- inspect(fit, what = "rsquare")["self_eff"] # extract rsquare
vif_self_eff <- 1 / (1 - r_self_eff) # compute vif

# Privacy Deliberation
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
SE01_01 ~~ a*SE01_02
SE01_03 ~~ a*SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

pri_delib ~ self_eff + pri_con + grats_gen + trust_spec

# Covariates
GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
r_pri_delib <- inspect(fit, what = "rsquare")["pri_delib"]
vif_pri_delib <- 1 / (1 - r_pri_delib)

## Privacy Concerns
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
SE01_01 ~~ a*SE01_02
SE01_03 ~~ a*SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

pri_con ~ self_eff + pri_delib + grats_gen + trust_spec

# Covariates
GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
r_pri_con <- inspect(fit, what = "rsquare")["pri_con"]
vif_pri_con <- 1 / (1 - r_pri_con)

# Gratifications
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
SE01_01 ~~ a*SE01_02
SE01_03 ~~ a*SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

grats_gen ~ self_eff + pri_con + pri_delib + trust_spec

# Covariates
GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
r_grats_gen <- inspect(fit, what = "rsquare")["grats_gen"]
vif_grats_gen <- 1 / (1 - r_grats_gen)

# Trust
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
SE01_01 ~~ a*SE01_02
SE01_03 ~~ a*SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

trust_spec ~ self_eff + pri_con + grats_gen + pri_delib

# Covariates
GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
r_trust_spec <- inspect(fit, what = "rsquare")["trust_spec"]
vif_trust_spec <- 1 / (1 - r_trust_spec)
```

```{r}
# Table
tibble("Gratifications" = vif_grats_gen, "Trust Specific" = vif_trust_spec, "Privacy Concerns" = vif_pri_con, "Privacy Deliberation" = vif_pri_delib, "Self-Efficacy" = vif_self_eff) %>% 
  kable() %>% 
  kable_styling("striped")
```

# Communication

In what follows, we report the results for the not-logged, that is the regular measure of communication.

## Model "Peregistered"

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

COMM ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec

# Covariates
COMM + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_prereg <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_prereg, fit = TRUE, std = TRUE)
rsquare_fit_prereg <- inspect(fit_prereg, what = "rsquare")["comm"]
```

## Model "Adapted"

Building on the preregistered model, instead of general gratifications and specific trust, we now use specific gratifications and general trust.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_gen =~ TR01_01 + TR01_05 + TR01_09

COMM ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen

# Covariates
COMM + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_05 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_adapted <- sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
summary(fit_adapted, fit = TRUE, std = TRUE)
rsquare_fit_adapted <- inspect(fit_adapted, what = "rsquare")["comm"]
```

## Model "Simple"

We now use only variables, that is specific gratifications and privacy concerns.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext

COMM ~ a1*pri_con + b1*grats_spec

# Covariates
COMM + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit_simple <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_simple, fit = TRUE, std = TRUE)
rsquare_fit_simple <- inspect(fit_simple, what = "rsquare")["comm"]
```

# Preregistered Model

We first analyze the same models as before, but analyzing self-disclosure instead of communication. This was how we initially preregistered the study.

## Model "Peregistered"

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

self_dis_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec

# Covariates
self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_prereg <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_prereg, fit = TRUE, std = TRUE)
rsquare_fit_prereg <- inspect(fit_prereg, what = "rsquare")["self_dis_log"]
```

## Model "Adapted"

Building on the preregistered model, instead of general gratifications and specific trust, we now use specific gratifications and general trust.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_gen =~ TR01_01 + TR01_05 + TR01_09

self_dis_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_05 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_adapted <- sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
summary(fit_adapted, fit = TRUE, std = TRUE)
rsquare_fit_adapted <- inspect(fit_adapted, what = "rsquare")["self_dis_log"]
```

## Model "Simple"

We now use only variables, that is specific gratifications and privacy concerns.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext

self_dis_log ~ a1*pri_con + b1*grats_spec

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit_simple <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_simple, fit = TRUE, std = TRUE)
rsquare_fit_simple <- inspect(fit_simple, what = "rsquare")["self_dis_log"]
```

Building on the Model "Adapted", we now remove the variable `Trust General`.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04

self_dis_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit, fit = TRUE, std = TRUE)
```

Interestingly, now almost all effects disappear. 

# Results without covariates

As stated in our preregistration, we also provide the results of all analyses without controlling for covariates. The results remain virtually the same.

### Model "Peregistered"

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

COMM_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec
"
fit_prereg <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_prereg, fit = TRUE, std = TRUE)
rsquare_fit_prereg <- inspect(fit_prereg, what = "rsquare")["comm"]
```

### Model "Adapted"

Building on the preregistered model, instead of general gratifications and specific trust, we now use specific gratifications and general trust.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_gen =~ TR01_01 + TR01_05 + TR01_09

COMM_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen
"
fit_adapted <- sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
summary(fit_adapted, fit = TRUE, std = TRUE)
rsquare_fit_adapted <- inspect(fit_adapted, what = "rsquare")["comm"]
```

### Model "Simple"

We now use only variables, that is specific gratifications and privacy concerns.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext

COMM_log ~ a1*pri_con + b1*grats_spec
"
fit_simple <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_simple, fit = TRUE, std = TRUE)
rsquare_fit_simple <- inspect(fit_simple, what = "rsquare")["comm"]
```

# Results including removed participants

As stated in the preregistration, we also report the analyses including the deleted participants. Results don't change meaningfully.

## Baseline model

```{r}
model_baseline <- "
  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
  grats_par =~ GR01_07 + GR01_08 + GR01_09
  grats_ide =~ GR01_10 + GR01_11 + GR01_12
  grats_ext =~ GR01_13 + GR01_14 + GR01_15
  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
  trust_gen =~ TR01_01 + TR01_05 + TR01_09
  trust_community =~ TR01_02 + TR01_03 + TR01_04
  trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
  trust_spec =~ trust_community + trust_provider
  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
    SE01_01 ~~ x*SE01_02
    SE01_03 ~~ x*SE01_04
  comm_log =~ COMM_log
  
  COMM_log ~~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec + f1*trust_gen + g1*grats_spec
"
fit_baseline <- sem(model_baseline, data = d_all, missing = "ML")
summary(fit_baseline, standardized = TRUE, fit.measures = TRUE)
```

```{r}
# extract model predicted values for items & calc means
d_fs <- lavPredict(fit_baseline, type = "ov") %>% 
  as.data.frame() %>% 
  mutate(version = d_all$version, 
         grats_gen_fs = rowMeans(select(., starts_with("GR02"))),
         grats_spec_fs = rowMeans(select(., starts_with("GR01"))), 
         pri_con_fs = rowMeans(select(., starts_with("PC01"))),
         trust_gen_fs = rowMeans(select(., TR01_01, TR01_05, TR01_09)),
         trust_spec_fs = rowMeans(select(., TR01_02: TR01_04, TR01_06 : TR01_12)),
         pri_del_fs = rowMeans(select(., starts_with("PD01"))),
         self_eff_fs = rowMeans(select(., starts_with("SE01")))) %>%
  select(version, pri_con_fs, grats_gen_fs, grats_spec_fs, pri_del_fs, self_eff_fs, trust_gen_fs, trust_spec_fs, COMM_log)

# combine d with d factor scores
d_all %<>% cbind(select(d_fs, -version, -COMM_log))
```

## Privacy calculus
## Model "Peregistered"

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

COMM_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec

# Covariates
COMM_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_prereg <- sem(model, data = d_all, estimator = "MLR", missing = "ML")
summary(fit_prereg, fit = TRUE, std = TRUE)
```

## Model "Adapted"

Building on the preregistered model, instead of general gratifications and specific trust, we now use specific gratifications and general trust.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_gen =~ TR01_01 + TR01_05 + TR01_09

COMM_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen

# Covariates
COMM_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_05 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_adapted <- sem(model, data = d_all, estimator = "MLR", missing = "ML", missing = "ML")
summary(fit_adapted, fit = TRUE, std = TRUE)
```

## Model "Simple"

We now use only variables, that is specific gratifications and privacy concerns.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext

COMM_log ~ a1*pri_con + b1*grats_spec

# Covariates
COMM_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit_simple <- sem(model, data = d_all, estimator = "MLR", missing = "ML")
summary(fit_simple, fit = TRUE, std = TRUE)
```

# Alternative Models

In what follows, you can find slightly different models that were also explored.

## Model 1

Here, we combine both privacy measures into a single one. Likewise, we combine both gratifications and trust. 

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
pri_cau =~ pri_con + pri_delib
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
grats_meta =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext + trust_community + trust_provider
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
self_dis_log ~ a1*pri_cau + b1*grats_meta + c1*self_eff

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit, fit = TRUE, std = TRUE)
```

## Model 2

Here, we combine both privacy measures into a single one. Likewise, we combine both gratifications and trust. 

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
pri_cau =~ pri_con + pri_delib
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
grats_meta =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext + trust_community + trust_provider
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
self_dis_log ~ a1*pri_cau + b1*grats_meta + c1*self_eff

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit, fit = TRUE, std = TRUE)
```

## Model 3

We now use also delete self-efficacy.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
pri_cau =~ pri_con + pri_delib
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
grats_meta =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext + trust_community + trust_provider
self_dis_log ~ a1*pri_cau + b1*grats_meta

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit, fit = TRUE, std = TRUE)
```

## Model 4

Here, we exchange specific gratitudes for general gratitudes.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05

self_dis_log ~ a1*pri_con + b1*grats_gen

# Covariates
self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit, fit = TRUE, std = TRUE)
```

